I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-04-22 lipics-master/comppaths.tex
update

\begin{table}[b!]
	\centering
	\begin{tabular}{|c|c|c|c|}
		\hline
		\text{Source/Target Layers}  &  \text{Natural DNN} & \text{Robust DNN} & \text{Ratio Natural vs Robust} \\ \hline \hline
		0 / 2 & 0.0304 & 0.00220  & 13.8x\\ \hline
		1 / 3  & 0.0313 & 0.00875 & 3.58x \\ \hline
		2 / 4  &  0.0267 & 0.00785 & 3.40x \\ \hline
		3 / 5  &  0.0253 & 0.00804  & 3.18x \\ \hline
	\end{tabular}
	\caption{Comparison of the average compensation strength over all the pairs of nodes of layer source/target between a DNN naturally-trained and a DNN robustly-trained using DiffAI \cite{DiffAI} with the same architecture and training set. {\color{red} Compensating strength with 1 layer between source and target is straightforward, and was sufficient to show the difference between DNNs trained naturally and by DiffAI.}}
	\label{tab:compensation}
\end{table}

@@

%		% Connect input to hidden layer
		\foreach \i in {3,4} {
			\foreach \h in {3,2} {
				\draw[line width=1pt, ->] (input\i) -- (hidden\h);
			}
		}

>>>>

\begin{table}[b!]
	\centering
	\begin{tabular}{|c|c|c|c|}
		\hline
		\text{Source/Target Layers}  &  \text{Natural DNN} & \text{Robust DNN} & \text{Ratio Natural vs Robust} \\ \hline \hline
		0 / 2 & 0.0304 & 0.00220  & 13.8x\\ \hline
		1 / 3  & 0.0313 & 0.00875 & 3.58x \\ \hline
		2 / 4  &  0.0267 & 0.00785 & 3.40x \\ \hline
		3 / 5  &  0.0253 & 0.00804  & 3.18x \\ \hline
	\end{tabular}
	\caption{Comparison of the average compensation strength over all the pairs of nodes of layer source/target between a DNN naturally-trained and a DNN robustly-trained using DiffAI \cite{DiffAI} with the same architecture and training set. {\color{red} Compensation strength with 1 layer between source and target is straightforward, and was sufficient to show the difference between DNNs trained naturally and by DiffAI.}}
	\label{tab:compensation}
\end{table}

@@

%		% Connect input to hidden layer
		\foreach \i in {3,4} {
			\foreach \h in {3,2} {
				\draw[line width=1.5pt, ->] (input\i) -- (hidden\h);
			}
		}
